Summary Tables

### 2020-03-03 summary_tables.Rmd
Add unit with distance and duration tables

  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
  cat("\n")

@@

### Baseline average distance (km) for all case studies
```{r}

@@

kable(trip_dist, caption = "Avg. distance per person (km) across all case studies")

@@

  print(city)
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 52, 3)))
  colnames(td)[3:7] <- rownames(scen_prop)

@@

## True Distance by total population
### Tables

@@

  print(kable(df, caption = paste("True distance by mode for  ", city)))
}

@@

## Duration tables
Case study specific duration tables for baseline and five scenarios

@@

  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))

@@

  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}

>>>>

  print(kable(td, caption = paste("Distance table (km) per day for ", city, "( ", count_people, " ) per person")))
  cat("\n")

@@

### Baseline average distance (km) per day for all case studies
```{r}

@@

kable(trip_dist, caption = "Avg. distance per person (km) per day across all case studies")

@@

  print(city)
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 365, 3)))
  colnames(td)[3:7] <- rownames(scen_prop)

@@

## True Distance by total population (per day in km)
### Tables

@@

  print(kable(df, caption = paste("True distance by mode per day for  ", city)))
}

@@

## Duration tables
Case study specific duration tables for baseline and five scenarios (per day in km)

@@

  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (everyone)")))

@@

  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}
